Open Data

### 2020-07-14 draft_chapter.Rmd
updated to nrow for points retrieved

If you are familiar with the shape of London then this image should be quite recognizable! We can now move on to scrape data from the Open Street Map API using the `opq()` function. The function name is short for 'Overpass query', which is how users can query the Open Street Map API using search criteria.

@@

This confirms details like the bounding box coordinates, but also provides information on the features collected from the query. As one might expect, most information relating to public transport station locations has been recorded using points (i.e. two-dimensional vertices, coordinates) of which we have over seven thousand at the time of writing. We also have around one hundred polygons. For now, let's extract the point information.

>>>>

If you are familiar with the shape of London then this image should be quite recognizable! We can now move on to query data from the Open Street Map API using the `opq()` function. The function name is short for 'Overpass query', which is how users can query the Open Street Map API using search criteria.

@@

This confirms details like the bounding box coordinates, but also provides information on the features collected from the query. As one might expect, most information relating to public transport station locations has been recorded using points (i.e. two-dimensional vertices, coordinates) of which we have `r nrow(osm_stat_sf$osm_points)` at the time of writing. We also have around one hundred polygons. For now, let's extract the point information.
